\PYGEOMETRY{}: a PYTHON library for the creation of Monte Carlo radiation transport physical geometries

### 2020-09-04 public/paper/pyg4ometry.tex
overlap checking algorithm
Paper update

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=6cm]{./diagrams/lattice}
\caption{The \fluka{lattice} feature demonstrating a \fluka{lattice} cell
  referring to its basic unit with the rototranslation $R_\textrm{trans}$.
  Any particle entering the cell will be transformed onto the basic unit
  with $R_\textrm{trans}$, and when leaving the basic unit, back to the cell
  with $R_\textrm{trans}^{-1}$.}
\label{fig:lattice}
\end{center}
\end{figure}

@@

\section{CAD/STL to GDML conversion }
STEP and IGES files can be loaded into \PYGEOMETRY{}, via an interface based on FreeCAD. FreeCAD is an 
open source CAD/CAM program, which in turn is based on OpenCASCADE. A STEP CAD file could be 
considered as a hierarchical tree of {\it part assemblies} and {\it part features}, where a part assembly is a 
collection of part features. A part feature can be used to create  a triangular mesh which can used to create 
a \PYGEOMETRY{} tessellated solid. Assignment of materials and visualisation attributes must be performed by 
the user after conversion to GDML as rarely will CAD/CAM packages included the detailed information required 
for RT codes.
\begin{lstlisting}[caption={A simple \PYGEOMETRY{} PYTHON script to load a STEP file.},label={lst:pythonCADLoading}, language=Python]
    reader = pyg4ometry.freecad.Reader("CadFileName.step")
    reader.relabelModel()
    reader.convertFlat()
    logical = reader.getRegistry().getWorldVolume()
\end{lstlisting}

>>>>

% part features
% part assembly

@@

\begin{figure}[hbtp]
\begin{center}
\includegraphics[width=6cm]{./diagrams/lattice}
\caption{The \fluka{lattice} feature demonstrating a \fluka{lattice} cell
  referring to its basic unit with the rototranslation $R_\textrm{trans}$.
  Any particle entering the cell will be transformed onto the basic unit
  with $R_\textrm{trans}$, and when leaving the basic unit, back to the cell
  with $R_\textrm{trans}^{-1}$.}
\label{fig:lattice}
\end{center}
\end{figure}

@@

\section{CAD/STL to GDML conversion }
STEP and IGES files can be loaded into \PYGEOMETRY{}, via an interface based on FreeCAD. FreeCAD is an 
open source CAD/CAM program, which in turn is based on OpenCASCADE. FreeCAD allows for scripting in PYTHON 
and acts as a simple to use interface to OpenCASCADE.A STEP CAD file could be 
considered as a hierarchical tree of part assemblies and part features, where a part assembly is a 
collection of part features. A part feature can be used to create a triangular mesh which can used to create 
a \PYGEOMETRY{} tessellated solid. Assignment of materials and visualisation attributes must be performed by 
the user after conversion to GDML as rarely will CAD/CAM packages included the detailed information required 
for RT codes. Listing~\ref{lst:pythonCADLoading} shows how \PYGEOMETRY can load step files.
\begin{lstlisting}[caption={A simple \PYGEOMETRY{} PYTHON script to load a STEP file.},label={lst:pythonCADLoading}, language=Python]
    reader = pyg4ometry.freecad.Reader("CadFileName.step")
    reader.relabelModel()
    reader.convertFlat()
    logical = reader.getRegistry().getWorldVolume()
\end{lstlisting}
